---
title: "Software"
toc: true
---

```{r}
#| label: startup
#| include: false

library(tidyverse)
library(lubridate)
library(pkgsearch)
library(DT)
library(cranlogs)
```

I have written a variety of [R packages](https://r-pkgs.org/) and have contributed to others. 

The sections below enumerate packages on [CRAN](https://cran.r-project.org/). Download statistics are from the Posit mirror of CRAN and are current as of `r today()`.

There are others that are unreleased, prototypes, or otherwise in-progress and these can be found on [my GitHub repositories page](https://github.com/topepo?tab=repositories&q=&type=source&language=&sort=).

```{r}
#| label: find-packages
#| include: false

check_authors <- function(x) {
 if (any(names(x) == "Authors@R")) {
  author_detail <- eval(parse(text = x$`Authors@R`))
 } else {
  author_detail <- x$Author
 }
 any(grepl("Max Kuhn", author_detail))
}

pick_url <- function(x, pkg) {
 if (is.na(x)) {
  return(cli::format_inline("https://CRAN.R-project.org/package={pkg}"))
 }
 x = gsub("\n", "", x)
 x <- strsplit(x, split = ",")[[1]]
 pkgdown <- grepl("(\\.io)|(\\.org)", x)
 if (any(pkgdown)) {
  x <- x[pkgdown]
 }
 x[1]
}

kuhn_pkgs <-
 advanced_search(Author = "kuhn", size = 100) %>%
 as_tibble() %>%
 mutate(its_a_me = map_lgl(package_data,check_authors)) %>%
 filter(its_a_me) %>%
 select(package, title, maintainer = maintainer_name, 
        `reverse dependencies` = revdeps, url) %>%
 mutate(
  url = map2_chr(url, package, pick_url),
  topic = glue::glue("<a href='{url}' target='_blank'>{package}</a>")
 ) %>% 
 mutate(package = factor(package)) %>%
 arrange(package)

downloads <-
 cran_downloads(kuhn_pkgs$package, from = ymd("2005-01-01"), to = today()) %>%
 summarize(downloads = sum(count), .by = c(package))

kuhn_pkgs <- 
 full_join(kuhn_pkgs, downloads, by = "package")
```

<br>

## CRAN Packages Maintained By Me

```{r}
#| label: max
#| echo: false
kuhn_pkgs %>% 
 filter(maintainer == "Max Kuhn") %>% 
 select(package = topic, title, `reverse dependencies`, downloads) %>% 
 datatable(rownames = FALSE,
           class = 'cell-border stripe',
           filter = 'top',
           escape = FALSE,
           options = list(pageLength = 25))
```


I also wrote the [odfWeave](https://cran.r-project.org/web/packages/odfWeave/index.html) package which I archived on 2018-04-19.

<br>

## CRAN Packages Maintained By Others

These packages are those that I have either oriiginally maintained, signficantly contributed to directly, or my code was included enough to be listed as a co-author: 

```{r}
#| label: others
#| echo: false
kuhn_pkgs %>% 
 filter(maintainer != "Max Kuhn") %>% 
 select(package = topic, title, maintainer, `reverse dependencies`, downloads) %>% 
 datatable(rownames = FALSE,
           class = 'cell-border stripe',
           filter = 'top',
           escape = FALSE,
           options = list(pageLength = 25))
```
